Variation in distance between consecutive animal locations

### 2021-04-05 distributions_paper/rudolph_distributions.Rmd
Editing methods

We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador. We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin]. Over a period of four years, from 2001 to 2005, *P. pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home]. Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes. Further details on field methods can be found in Holbrook [-@holbrook2011home]. It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15. <span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions. We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded. This gave us a total of **600ish?** data points for turning angles and velocities.red</span>

@@

However, it is not as straight-forward since there are multiple competing models for certain individuals, which we consider as those within less than 2 units of the delta AIC or BIC. When using AIC, there are competing models for almost every individual, whereas with BIC, only 4 of the individuals have competing models. 
```{r fig.width=12, fig.height=4}
# To visualize the differences in the information criteria at the individual level

>>>>

We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador. We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin]. Over a period of four years, from 2001 to 2005, *P. pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home]. Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes. Further details on field methods can be found in Holbrook [-@holbrook2011home]. It is important to note that these methods did not track all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15. From the relocation data, we calculated animal trajectories by considering discrete steps between successive relocations of each animal [@turchin1998quantitative], quantifying their turning angle after each movement, estimating the Euclidean distance between successive relocations, and estimating the velocity for each segment as the displacement distance divided by the length of the time interval. We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate the descriptive parameters for each trajectory, such as turning angles and net squared displacement.

# Results  
The majority of trajectories obtained were regular, with 15 minute time lags between successive relocations, however, some relocations were gathered at different time intervals, making them irregular. To analyze all trajectories and compare their descriptive parameters, we decided to work under a velocity-based framework.

<span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions. We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded. This gave us a total of **600ish?** data points for turning angles and velocities.red</span>

@@

However, it is not as straight-forward since there are multiple competing models for certain individuals, which we consider as those within less than 2 units of the delta AIC or BIC. When using AIC, there are competing models for almost every individual, whereas with BIC, only 4 of the individuals have competing models. We should use 4 for BIC and 3 for AIC. Look for the paper Taper Ponciano 2016. 
```{r fig.width=12, fig.height=4}
# To visualize the differences in the information criteria at the individual level
